Relevance Modeling with Documents Expanded Using External Collections

### 2017-02-18 paper.tex
clarified section on sensitivity to n

Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for each target collection using our established cross-validation procedure with identical folds. The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections. We therefore choose the value of 10 as an apparently safe value; this is a convenient result since it allows for more efficient document expansion.

>>>>

Figure \ref{figure.n-sweeps} shows sweeps over several values of $n$, the number of expansion documents, for the \textit{single} and \textit{wiki} QL runs using our established cross-validation procedure with identical folds. The sensitivity to $n$ is not pronounced at $n \geq 5$, and what little variation exists is not consistent across collections. We therefore set the value of 10, an apparently safe value, for all other runs. This is a convenient result since it allows for more efficient document expansion.
